Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-04 robdml.tex
p2

\textbf{Adversarial Defense.}
%
To battle against the attacks, some early defenses incur gradient masking
effect, but it gives a false sense of security~\cite{obfuscated}.
%
Defensive distillation~\cite{distill2} can be compromised~\cite{cw}.
%
Ensemble of weak defenses is not robust~\cite{ensembleweak}.
%
Other forms of defenses are also proposed, such as input
preprocessing~\cite{deflecting}, or a randomization inside the
network~\cite{self-ensemble}.
%
But various defense methods are still susceptible to adaptive
attack~\cite{adaptive}.
%
Of all defenses, adversarial training remains to be one of the most
effective method~\cite{bilateral,advtrain-triplet,benchmarking}, and it
consistently show promising empirical robustness,
although suffering from significant training cost and a lower performance
on benign examples.

\textbf{Deep Metric Learning.}
%
A wide range of applications such as image retrieval~\cite{imagesim2},
cross-modal retrieval~\cite{ladderloss}, and face recognition~\cite{facenet}
can be formulated as Deep Metric Learning.
%
A well-designed loss function is crucial for DML performance~\cite{dmlreality}.
As suggested by recent study, the classical triplet loss could reach
state-of-the-art performance with an appropriate triplet sampling
strategy~\cite{revisiting}.

>>>>

\textbf{Adversarial Defense.}
%
To battle against the attacks, some defenses incur gradient masking
effect, but leads to a false sense of security~\cite{obfuscated}.
%
Defensive distillation~\cite{distill2} is compromised~\cite{cw}.
%
Ensemble of weak defenses is not robust~\cite{ensembleweak}.
%
Other defenses are also proposed, such as input
preprocessing~\cite{deflecting}, or a randomization inside the
network~\cite{self-ensemble}.
%
But many defenses are still susceptible to adaptive attack~\cite{adaptive}.
%
Of all defenses, adversarial training remains to be one of the most effective
method~\cite{bilateral,advtrain-triplet,benchmarking}, consistently showing
promising empirical robustness, although suffers from high training
cost and a performance drop on benign examples.

\textbf{Deep Metric Learning.}
%
A wide range of applications such as image retrieval~\cite{imagesim2},
cross-modal retrieval~\cite{ladderloss}, and face recognition~\cite{facenet}
can be formulated as Deep Metric Learning.
%
A well-designed loss function and a proper sampling method are crucial for DML
performance~\cite{dmlreality}.  As suggested by recent study, the classical
triplet loss could reach state-of-the-art performance with an appropriate
triplet sampling strategy~\cite{revisiting}.
